---
title: "finalPrez"
author: "Elise, Steph, Mitchell"
date: "March 4, 2016"
output: ioslides_presentation
runtime: shiny
theme: readable
---

```{r setup, echo=F}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(ggvis))

```

## Team Pollute

- Our dataset
- Introduce your topic, providing specific scientific questions and problem statements.

## Goals

- Clearly communicate hotspots of pollution in the EU
- Find differences in pollution levels between rural and urban areas
- Discover which countries/cities exceed pollution standards

## Pollution Hotspots

```{r Pollution Hotspots}

```

## Rural vs Urban

```{r Rural vs Urban, echo=F}
pollutants = c("PM10", "NO2", "O3", "PM2.5", "BaP", "SO2")
for  (i in 1:length(pollutants)){
  DataTable = read_excel('data/EU2013.xlsx', sheet=i)%>%
    mutate(areatype= `station_type_of_area`)%>%
    mutate(pol=pollutants[i])
  
  assign(pollutants[i],DataTable)
}

poltot = bind_rows(list(PM10, NO2, O3, PM2.5, BaP, SO2))
```

```{r ru shiny, echo=F}
library(shiny)
ui = fluidPage(
  titlePanel("title panel"),
  
  sidebarLayout(position = "right",
                sidebarPanel( "sidebar panel"),
                mainPanel("main panel")),
  
  sliderInput(inputId = "n_breaks",
              label = "Number of bins:",
              min = 1,
              max = 50,
              value = 30),
  
  actionButton("action", label = "Action"),
  
  plotOutput(outputId = "main_plot", height = "300px"))

server = function(input, output) {
  
  output$main_plot <- renderPlot({
    
    hist(faithful$eruptions,
         probability = TRUE,
         breaks = as.numeric(input$n_breaks),
         xlab = "Duration (minutes)",
         main = "Geyser eruption duration",
         col = "lightblue")
    
  })
  
}
shinyApp(ui, server)
```

## Pollution Advistories

```{r Pollution Advistories, echo = TRUE}

```
