---
title: "Team Pollute"
author: "Elise, Steph, Mitchell"
date: "March 4, 2016"
output: ioslides_presentation
runtime: shiny
theme: readable
---

```{r setup, echo=F}
suppressPackageStartupMessages(library(plyr))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(ggvis))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(gridExtra))
```

## Team Pollute

- Our dataset
- Introduce topic, providing specific scientific questions and problem statements.

## Goals

- Clearly communicate hotspots of pollution in the EU
- Find differences in pollution levels between urban and suburban areas
- Discover which countries/cities exceed pollution standards

## Pollution Hotspots

```{r Pollution Hotspots,echo=F,message=FALSE}
suppressPackageStartupMessages(library(googleVis))

library(shiny)
library(googleVis)
library(RCurl)
library(readxl)
library(dplyr)
library(shinydashboard)

pollutants = c("PM10", "NO2", "O3", "PM2.5", "BaP", "SO2")
statistic= c('Mean','Maximum')

#setup data table for map
for  (i in 1:length(pollutants)){
  DataTable = read_excel('EUPollute/data/EU2013.xlsx', sheet=i)%>%
    mutate(iso2c= `country iso code`)%>%
    group_by(iso2c)%>%
    summarise("Limit"=max(Limit),"LimitText"=max(LimitText),"Mean"=round(mean(statistic_value), digits = 2),"Maximum"=round(max(statistic_value), digits = 2))%>%
    mutate(pol=pollutants[i])
  
  
  assign(pollutants[i],DataTable)
}

poltot = bind_rows(list(PM10, NO2, O3, PM2.5, BaP, SO2))



  MaxTable = poltot%>%
    group_by(pol)%>%
    summarise("value"=max(Maximum,na.rm=TRUE))
  
  

maxvalues=data.frame(t(MaxTable[,2]))
colnames(maxvalues)=(t(MaxTable[,1]))

####################
# Shiney App
####################

# Define UI for application that draws a histogram
ui <- dashboardPage(

  dashboardHeader(disable = TRUE),
  dashboardSidebar(disable = TRUE),
  

   # Sidebar with a slider input for number of bins
  dashboardBody(
    fluidRow(
      column(width = 3,
         selectInput("dataset",
                     "Pollutant to display:",
                     pollutants),
         
         selectInput("statistic",
                     "Statistic to display:",
                     statistic)),
       column(width=5,
              box(width=12,
         actionButton("Above", "Normalize to Limit")),
         box(width=12,
         actionButton("Reset", "Normalize to Minimum (reset)"))),
       column(width=4,
         htmlOutput("LimitText"))
         ),

      # Show a plot of the generated distribution
       
    fluidRow(
      column(height=600, width=12, 
        box(width=NULL,
            title = "European Air Pollutants (2013)",
            status = "primary",
          htmlOutput("Map")))
    )
    )
)






# Define server logic
server <- function(input, output, session) {

  #select by pollution
  datasetPol=reactive({
    switch(input$statistic,
           "Mean"=poltot%>%
                  filter(pol==input$dataset)%>%
                  mutate("value"=Mean),
           
           "Maximum"=poltot%>%
                    filter(pol==input$dataset)%>%
                    mutate("value"=Maximum)
    )
  })
  
#creates text for limits 
  Limitinfo=reactive({
    as.character(summarise(datasetPol(),max(LimitText,na.rm=TRUE)))
  })
    
  
#initialize limits
  limits=reactiveValues(data =NULL)
#reset limits after changing selection
observeEvent(input$dataset,{
  limits$data=c(min(datasetPol()$value,na.rm=TRUE),max(datasetPol()$value,na.rm=TRUE))
})
observeEvent(input$Reset,{
  limits$data=c(min(datasetPol()$value,na.rm=TRUE),max(datasetPol()$value,na.rm=TRUE))
})
observeEvent(input$statistic,{
  limits$data=c(min(datasetPol()$value,na.rm=TRUE),max(datasetPol()$value,na.rm=TRUE))
})

#reset limits after selecting above limit
observeEvent(input$Above,{
     limits$data=c(max(datasetPol()$Limit,na.rm=TRUE),
                   max(max(datasetPol()$Limit,na.rm=TRUE)+1,max(datasetPol()$value,na.rm=TRUE)))
    })
   
   #create map
   output$Map <- renderGvis({

     gvisGeoChart(
       datasetPol(),
       locationvar = "iso2c", 
       colorvar = input$statistic,
        options=list(
          title ="Concentrations",
          region='150',
          backgroundColor.fill = "#BDBDBD",
          height=450,
          width=700,
          colorAxis=paste0("{minValue:", limits$data[1],",maxValue:",limits$data[2],", colors:['#1a9641','#ffffb2', '#ef3b2c', '#99000d']}"),
          datalessRegionColor='#F5F5F5'

          ))

   })

   output$LimitText <- renderUI({
     HTML(paste("<p><b>European Limits for Pollutant:</b></p>", Limitinfo(), sep="<br/>"))
   })
   }
   
# Run the application
shinyApp(ui = ui, server = server)
```

## Pollutant Levels: Urban vs Suburban

```{r Urb v Sub, echo=F}

pollutants = c("PM10", "NO2", "O3", "PM2.5", "BaP", "SO2")

library(shiny)
ui = fluidPage(
  
    selectInput("dataset", "Pollutant:", pollutants),
    uiOutput("text1"),
    plotOutput("main_plot", height = "300px", width = "600px"),
    tableOutput('table1'),
    paste("Comparison between urban and suburban was done with a quick-and-dirty two-sample t-test, alpha = 0.05. Assumptions were not tested.")
)

server = function(input, output) {
  
  # Data wrangling
  for  (i in 1:length(pollutants)){
    DataTable = read_excel('data/EU2013.xlsx', sheet=i) %>%
      filter(!is.na(`country iso code`)) %>%
      rename(`Area Type` = station_type_of_area) %>%
      mutate(pol=pollutants[i])
  
    assign(pollutants[i],DataTable)
}

  poltot = bind_rows(list(PM10, NO2, O3, PM2.5, BaP, SO2))
    
  # Reactive assignment for pollution type
  datasetInput = reactive({
    filter(poltot, pol==input$dataset) 
  })

  # Reactive assignmet for means lines in histogram
  means = reactive({
    ddply(
      datasetInput(), 
      "`Area Type`", 
      summarise, 
      Mean=mean(statistic_value, na.rm=T)
    )
  })
    
  # The histogram
  output$main_plot <- renderPlot({
    
    ggplot(data=datasetInput(), aes(statistic_value, fill = `Area Type`)) +
      geom_histogram(alpha = 0.55, aes(y = ..density..), position = 'identity', bins = 16) +
      theme_bw() +
      theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
      labs(x = "Mean Annual Concentration (micrograms per cubic meter)") +
      scale_fill_manual(values=c("honeydew 4", "#E69F00")) +
      geom_vline(data=means(), aes(xintercept = Mean, color = `Area Type`), size = 1.5) +
      scale_color_manual(values=c("black", "peru"))

  })

  # Data Wrangling for the Stats

  x = reactive({
    filter(poltot, `Area Type`=='urban', pol==input$dataset) %>% .$statistic_value
  })
  
  y = reactive({
    filter(poltot, `Area Type`=='suburban', pol==input$dataset) %>% .$statistic_value
  })
  
  pval = reactive({
    t.test(x(), y(), alternative = "two.sided")$p.value
  })

  # Text Output
  
  output$text1 <- renderUI({
    if(pval() > 0.05){
      not = strong('NOT')
    } else {
      not = ''
    }
    
    if(pval() > 0.001){
      pvalrend = sprintf('= %0.3f', pval()) # The f is for 'floating point' to place the decimal
    } else {
      pvalrend = '< 0.001'
    }
    
    HTML(sprintf('%s values did %s differ significiantly between urban and suburban areas. (p %s)', input$dataset, not, pvalrend))
  })
  
  # Table Output

  output$table1 <- renderTable({
    means()
  },
  include.rownames=FALSE)

}
  
shinyApp(ui, server)
```

## Pollution Advisories: a quick data overview

```{r Pollution Advisories, echo = F,message=FALSE,warning=FALSE}
 library(gridExtra)
 
# #WHO Air Quality Guidelines (annual mean, in ug/m3):
 AQG.PM2.5 = 10
 AQG.NO2 = 40
 AQG.BaP = 0.001
# #Currently, no WHO guidelines for benzo[a]pyrene levels. BaP level from EU standards (2012). EU does not measure PM10, SO2, and O3 do not per WHO guidelines.
 
# # Determine which countries have sites exceeding WHO Air Quality Guidelines. Red line on graphs indicate AQG for annual mean concentration.
PM10 = read_excel('data/EU2013.xlsx', sheet=1) 
 
 PM10plot = ggplot(PM10, aes(x=city_name, y=statistic_value)) + geom_point(show.legend = T) + geom_hline(yintercept = AQG.PM10, color = 'red') + ggtitle('PM10') + xlab('Measurement Site') + ylab('PM10 Concentration (ug/m3)')
 
 
NO2 = read_excel('data/EU2013.xlsx', sheet=2)
 
 NO2plot = ggplot(NO2, aes(x=city_name, y=statistic_value)) + geom_point(show.legend = T) + geom_hline(yintercept = AQG.NO2, color = 'red') + ggtitle('NO2') + xlab('Measurement Site') + ylab('NO2 Concentration (ug/m3)')
 
 
O3 = read_excel('data/EU2013.xlsx', sheet=3)
 
 O3plot = ggplot(O3, aes(x=city_name, y=statistic_value)) + geom_point(show.legend = T) + geom_hline(yintercept = AQG.O3, color = 'red') + ggtitle('O3') + xlab('Measurement Site') + ylab('O3 Concentration (ug/m3)')

 
PM2.5 = read_excel('data/EU2013.xlsx', sheet=4)
  
 PM2.5plot = ggplot(PM2.5, aes(x=city_name, y=statistic_value)) + geom_point(show.legend = T) + geom_hline(yintercept = AQG.PM2.5, color = 'red') + ggtitle('PM2.5') + xlab('Measurement Site') + ylab('PM2.5 Concentration (ug/m3)')
 
 
SO2 = read_excel('data/EU2013.xlsx', sheet=6)
 
 SO2plot = ggplot(SO2, aes(x=city_name, y=statistic_value)) + geom_point(show.legend = T) + geom_hline(yintercept = AQG.SO2, color = 'red') + ggtitle('SO2') + xlab('Measurement Site') + ylab('SO2 Concentration (ug/m3)')
 
BaP = read_excel('data/EU2013.xlsx', sheet=5)
  
 BaPplot = ggplot(BaP, aes(x=city_name, y=statistic_value)) + geom_point(show.legend = T) + geom_hline(yintercept = AQG.BaP, color = 'red') + ggtitle('BaP') + xlab('Measurement Site') + ylab('BaP Concentration (ug/m3)')
# 
grid.arrange(PM2.5plot, NO2plot, BaPplot, nrow=1)
```

## Advisory Spots. Which cities/countries have the worst air quality levels?

```{r Advisory Spots, echo = F,message=FALSE}
Data = read_excel('data/AllAirData.xlsx')

Subset = subset(Data, select=c(iso, city_name, component_caption, statistic_value))

Table=datatable(Subset, 
                style = 'bootstrap',
                options = list(dom = 'tip',pageLength = 4, autoWidth = TRUE), 
                filter = 'top', 
                colnames = c('Country' = 'iso', 'City' = 'city_name', 'Pollutant Type' = 'component_caption', 'Statistic value (ug/m3)' = 'statistic_value'),
                caption = 'Air Pollutants in the EU'
                )



Table
```
