---
title: "Team Pollute"
author: "Elise, Steph, Mitchell"
date: "March 4, 2016"
output: ioslides_presentation
runtime: shiny
theme: readable
---

```{r setup, echo=F}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(ggvis))
suppressPackageStartupMessages(library(ggplot2))
```

## Team Pollute

- Our dataset
- Introduce your topic, providing specific scientific questions and problem statements.

## Goals

- Clearly communicate hotspots of pollution in the EU
- Find differences in pollution levels between rural and urban areas
- Discover which countries/cities exceed pollution standards

## Pollution Hotspots

```{r Pollution Hotspots}

```

## Rural vs Urban

```{r Rural vs Urban, echo=F}
pollutants = c("PM10", "NO2", "O3", "PM2.5", "BaP", "SO2")
for  (i in 1:length(pollutants)){
  DataTable = read_excel('data/EU2013.xlsx', sheet=i)%>%
    mutate(areatype= toupper(`type_of_station`))%>%
    mutate(pol=pollutants[i])
  
  assign(pollutants[i],DataTable)
}

poltot = bind_rows(list(PM10, NO2, O3, PM2.5, BaP, SO2))
```

```{r ru shiny, echo=F}
library(shiny)
ui = fluidPage(

  selectInput("dataset", "Pollutant to display:", pollutants),
  
  plotOutput(outputId = "main_plot", height = "300px"))

server = function(input, output) {
  
    datasetInput = reactive({
     filter(poltot,pol==input$dataset)
     })
  
  output$main_plot <- renderPlot({
    
    ggplot(datasetInput(), aes(statistic_value, fill = areatype)) +
      geom_histogram(alpha = 0.5, aes(y = ..density..), position = 'identity', bins = 16) +
      theme_bw()

  })
  
  
}
shinyApp(ui, server)
```

## Pollution Advistories

```{r Pollution Advistories, echo = TRUE}

```
