---
title: "Team Pollute"
author: "Elise, Steph, Mitchell"
date: "March 4, 2016"
output: ioslides_presentation
runtime: shiny
theme: readable
---

```{r setup, echo=F}
suppressPackageStartupMessages(library(plyr))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(ggvis))
suppressPackageStartupMessages(library(ggplot2))
```

## Team Pollute

- Our dataset
- Introduce topic, providing specific scientific questions and problem statements.

## Goals

- Clearly communicate hotspots of pollution in the EU
- Find differences in pollution levels between background and traffic areas
- Discover which countries/cities exceed pollution standards

## Pollution Hotspots

```{r Pollution Hotspots}

```

## Background vs Traffic

```{r BG vs Traffic, echo=F}

pollutants = c("PM10", "NO2", "O3", "PM2.5", "BaP", "SO2")

library(shiny)
ui = fluidPage(

  selectInput("dataset", "Pollutant:", pollutants),
  
  # selectInput("area", "Distinction:", c("Urban vs Suburban", "Background vs Traffic")),
  
  plotOutput(outputId = "main_plot", height = "300px")
  
  )

server = function(input, output) {
  
  # Data wrangling
  for  (i in 1:length(pollutants)){
    DataTable = read_excel('data/EU2013.xlsx', sheet=i) %>%
      mutate(pol=pollutants[i])
  
    assign(pollutants[i],DataTable)
}

    poltot = bind_rows(list(PM10, NO2, O3, PM2.5, BaP, SO2))

    # # Reactive assignment for distinction... can't figure out how to make this switch, screw it.
    # areaInput = reactive({
    #   switch(input$area, 
    #                    "Urban vs Suburban" = station_type_of_area,
    #                    "Background vs Traffic" = type_of_station
    #                    )
    #   
    #   poltot = mutate(poltot, `Area Type` = areaInput())
    # })
    
    # Reactive assignment for pollution type
    datasetInput = reactive({
     filter(poltot, pol==input$dataset) })

    # Reactive assignmet for means lines in histogram
    means = reactive({
      ddply(
        datasetInput(), 
        "station_type_of_area", 
        summarise, 
        data.mean=mean(statistic_value, na.rm=T)
        )
    })
    
    # The histogram
  output$main_plot <- renderPlot({
    
    ggplot(data=datasetInput(), aes(statistic_value, fill = station_type_of_area)) +
      geom_histogram(alpha = 0.55, aes(y = ..density..), position = 'identity', bins = 16) +
      theme_bw() +
      theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
      labs(x = "Mean Annual Concentration (micrograms per cubic meter)") +
      scale_fill_manual(values=c("honeydew 4", "#E69F00")) +
      geom_vline(data=means(), aes(xintercept = data.mean, color = station_type_of_area), size = 1.5) +
      scale_color_manual(values=c("black", "peru"))

  })
  
}
  
shinyApp(ui, server)
```

## Pollution Advisories

```{r Pollution Advisories, echo = TRUE}

```
