---
title: "finalPrez"
author: "Elise, Steph, Mitchell"
date: "March 4, 2016"
output: ioslides_presentation
theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Team Pollute

- Our dataset
- Introduce your topic, providing specific scientific questions and problem statements.

## Goals

- Clearly communicate hotspots of pollution in the EU
- Find differences in pollution levels between rural and urban areas
- Discover which countries/cities exceed pollution standards

## Pollution Hotspots

```{r Pollution Hotspots}

```

## Rural vs Urban

```{r Rural vs Urban}

```

## Pollution Advisories

```{r Pollution Advisories, echo = TRUE}
library(readr)
library(dplyr)
library(readxl)
library(RCurl)
library(devtools)
library(gridExtra)
library(jsonlite)
library(htmltools)
library(ggplot2)
#WHO Air Quality Guidelines (annual mean, in ug/m3):
AQG.PM10 = 20
AQG.PM2.5 = 10
AQG.NO2 = 40
AQG.O3 = 100
AQG.SO2 = 20
#Currently, no WHO guidelines for benzo[a]pyrene levels.

# Determine which countries have sites exceeding WHO Air Quality Guidelines. Red line on graphs indicate AQG for annual mean concentration.
PM10 = read_excel('EU2013.xlsx', sheet=1) 

PM10plot = ggplot(PM10, aes(x=city_name, y=statistic_value)) + geom_point(show.legend = T) + geom_hline(yintercept = AQG.PM10, color = 'red') + ggtitle('PM10') + xlab('Measurement Site') + ylab('PM10 Concentration (ug/m3)')
windows()
PM10plot

NO2 = read_excel('EU2013.xlsx', sheet=2)

NO2plot = ggplot(NO2, aes(x=city_name, y=statistic_value)) + geom_point(show.legend = T) + geom_hline(yintercept = AQG.NO2, color = 'red') + ggtitle('NO2') + xlab('Measurement Site') + ylab('NO2 Concentration (ug/m3)')
windows()
NO2plot

O3 = read_excel('EU2013.xlsx', sheet=3)

O3plot = ggplot(O3, aes(x=city_name, y=statistic_value)) + geom_point(show.legend = T) + geom_hline(yintercept = AQG.O3, color = 'red') + ggtitle('O3') + xlab('Measurement Site') + ylab('O3 Concentration (ug/m3)')
windows()
O3plot

PM2.5 = read_excel('EU2013.xlsx', sheet=4)
 
PM2.5plot = ggplot(PM2.5, aes(x=city_name, y=statistic_value)) + geom_point(show.legend = T) + geom_hline(yintercept = AQG.PM2.5, color = 'red') + ggtitle('PM2.5') + xlab('Measurement Site') + ylab('PM2.5 Concentration (ug/m3)')
windows()
PM2.5plot

SO2 = read_excel('EU2013.xlsx', sheet=6)

SO2plot = ggplot(SO2, aes(x=city_name, y=statistic_value)) + geom_point(show.legend = T) + geom_hline(yintercept = AQG.SO2, color = 'red') + ggtitle('SO2') + xlab('Measurement Site') + ylab('SO2 Concentration (ug/m3)')
windows()
SO2plot

windows()
grid.arrange(PM10plot, PM2.5plot, NO2plot, SO2plot, O3plot, nrow=2)
```
